% ************************** Thesis Acknowledgements **************************

\vspace{-18pt}
\begin{center}
    \begin{minipage}[t]{0.8\textwidth}
    \centering
    \par\noindent\rule{0.9\textwidth}{0.4pt} \\
    ``One, remember to look up at the stars and not down at your feet. Two, never give up work. Work gives you meaning and purpose and life is empty without it. Three, if you are lucky enough to find love, remember it is there and don't throw it away.'' \\
    ---\textit{Stephen Hawking}
    \par\noindent\rule{0.9\textwidth}{0.4pt} \\
\end{minipage}
\end{center}

\vspace{18pt}

First of all, I would like to thank all the people I worked with during my PhD.
I thank my PhD supervisor Graham Taylor for providing an excellent environment to grow as a better researcher and a better person. His patience, knowledge, open-mindedness and gentle guidance helped me immensely starting from the very first days of my PhD. I would like to thank Graham for connecting me with other wonderful people. In particular, I am deeply thankful to work with Mohamed Amer during my first internship. Mohamed treated me as a friend providing support and advice beyond the work related challenges. I really appreciate the flexibility and amount of time he gave me to explore different research directions. This helped me tremendously in gaining necessary knowledge to progress in my PhD. 

In the middle of my PhD I got an opportunity to intern at MILA with amazing people, Eugene Belilovsky and Aaron Courville, as well as our collaborators, Harm de Vries and C{\u{a}}t{\u{a}}lina Cangea. I learned a lot from them in terms of knowledge and collaboration skills. I am especially grateful to Eugene for his deep involvement in the projects and helping in publishing the results. This internship also allowed me to explore the unique AI ecosystem of MILA as well as life in the Quebec province and Montreal to make important career decisions after that.

After MILA, I was extremely lucky to intern at Facebook AI (currently Meta AI) with nice and smart people, Adriana Romero-Soriano and Michal Drozdzal. I thank them for giving me the right amount of flexibility in doing my research, for asking me difficult questions and for staying closely involved in the project beyond the internship. Adriana and Michal greatly improved my critical thinking, writing and collaboration skills. Their feedback and guidance was crucial to successfully finalize my last PhD project.

I would like to express gratitude to other people I collaborated and interacted with: Xiao Lin, Carolyn Augusta, Chris Kim, Yichao Lu, Himanshu Rai, Jason Chang, Shashank Shekhar, Maksims Volkovs, Hyunsoo Chung, Jungtaek Kim, Jinhwi Lee, Jaesik Park, Minsu Cho, Elahe Ghalebi and Rylee Thompson. Doing research and writing papers together with you was a very smooth, pleasant and useful experience. I hope I was not a big burden in our projects. I am very grateful to my advisory committee members, Shawki Areibi and Medhat Moussa, for their prompt feedback and support. I am also extremely thankful to lab managers Brittany Reiche and Magdalena Sobol for their support and patience. I thank Magdalena for shaping my writing style and presentation skills.

I am expressing my gratitude to my labmates at Machine Learning Research Group whom I met in person in the beginning of my PhD making the first months in a new country less challenging for me.
Unfortunately, due to the pandemic I could not meet in person many other kind and smart members of our lab. 

I am thankful to the Government of Canada, Ontario and Quebec provinces, University of Guelph and Vector Institute for being very welcoming, transparent, responsive and for providing necessary computing resources, support and funding to work on my PhD.

Finally and most importantly, my PhD could not be completed without the support, care and love from my family, my parents, my wife and children. Doing a PhD is extremely stressful, frustrating, demanding and prone to high overtimes hurting both physical and mental health. I am very thankful to my wife for making my work-family balance good and stable. This encouraged me to work more efficiently and allowed me to finish my PhD without big sacrifices. I also deeply appreciate her patience of living far away from her home, parents and friends in a country that she struggles to fully enjoy to let me realize my potential. This means a lot to me! 
