\noindent This thesis is based on the following publications:

\begin{enumerate}
    \item \textbf{Knyazev, B.}, Taylor, G.~W., and Amer, M.~(2019). Understanding attention and generalization in graph neural networks. In Advances in Neural Information Processing Systems (NeurIPS). Code: \url{https://github.com/bknyaz/graph_attention_pool}.
    
    %\begin{itemize}
    %\item 
    
    %\end{itemize}
    
    \item \textbf{Knyazev, B.}, de Vries, H., Cangea, C., Taylor, G.~W., Courville, A., and Belilovsky, E.~(2020). Graph density-aware losses for novel compositions in scene graph generation. British Machine Vision Conference (BMVC). 
    %
    Code: \url{https://github.com/bknyaz/sgg}.
    
    \item \textbf{Knyazev, B.}, de Vries, H., Cangea, C., Taylor, G.~W., Courville, A., and Belilovsky, E.~(2021). Generative compositional augmentations for scene graph prediction. In International Conference on Computer Vision (ICCV). 
    %
    Code: \url{https://github.com/bknyaz/sgg}.
    
    \item \textbf{Knyazev, B.}, Drozdzal, M.$^\dagger$, Taylor, G.~W.$^\dagger$, and Romero-Soriano, A.$^\dagger$~(2021). Parameter prediction for unseen deep architectures. In Advances in Neural Information Processing Systems (NeurIPS).
    %
    Code: \url{https://github.com/facebookresearch/ppuda}.
\end{enumerate}

In the works listed above, the contributions of the first author are the following: developed the key components of algorithms and models; developed the code; designed and ran most of the experiments; and wrote the key sections of the papers. All the works above include the associated source code and the publicly accessible link is specified.

\vspace{18pt}
\noindent The author has also contributed to the following publications and technical reports:

\begin{enumerate}
    \item \textbf{Knyazev, B.}, Lin, X., Amer, M.~R., and Taylor, G.~W.~(2018). Spectral multigraph networks for discovering and fusing relationships in molecules. In NeurIPS Workshop on Machine Learning for Molecules and Materials.
    %
    Code: \url{https://github.com/bknyaz/graph_nn}.
    
    \item \textbf{Knyazev, B.}, Lin, X., Amer, M.~R., and Taylor, G.~W.~(2019). Image classification with hierarchical multigraph networks. In British Machine Vision Conference (BMVC). %\looseness-1
    %
    Code: \url{https://github.com/bknyaz/bmvc_2019}.
    
    \item \textbf{Knyazev, B.}\textsuperscript{*}, Augusta, C.\textsuperscript{*}, and Taylor, G.~W.~(2021). Learning temporal attention in dynamic graphs with bilinear interactions. PLOS ONE, 16(3):1–18.
    %
    Code: \url{https://github.com/uoguelph-mlrg/LDG}.
    
    \item Lu, Y., Rai, H., Chang, J., \textbf{Knyazev, B.}, Yu, G., Shekhar, S., Taylor, G.~W., and Volkovs, M.~(2021). Context-aware scene graph generation with seq2seq transformers. In International Conference on Computer Vision (ICCV).
    %
    Code: \url{https://github.com/layer6ai-labs/SGG-Seq2Seq}.
    
    \item Chung, H., Kim, J., \textbf{Knyazev, B.}, Lee, J., Taylor, G.~W., Park, J., and Cho, M.~(2021). Brick-by-brick: Combinatorial construction with deep reinforcement learning. In Advances in Neural Information Processing Systems (NeurIPS).
    %
    Code: \url{https://github.com/POSTECH-CVLab/Brick-by-Brick}.
    
    
    \item Thompson, R., \textbf{Knyazev, B.}, Ghalebi, E., Kim, J., Taylor, G.~W.~(2021). On Evaluation Metrics for Graph Generative Models. In International Conference on Learning Representations (ICLR). 
    %
    Code: \url{https://github.com/uoguelph-mlrg/GGM-metrics}.
    
    
\end{enumerate}

\noindent In the lists above, equal contribution is denoted by \textsuperscript{*}, and equal advising is denoted by $^\dagger$.